Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-15 ms.tex
Noted that Delta chi^2=5.89 is the 1-sigma region for a 5D fit and changed the plots to show samples within Delta chi^2 < 5.89.

correlated (anticorrelated) with halo concentration at fixed $\mvir.$ Thus the $A_{\rm cen,sat}$ parameters span the range $[-1, 1].$ 

@@

%----------------------------------------------------------------------------------------------------------------------------------
\begin{figure*}
\begin{center}
\includegraphics[width=8.3cm]{Mr19samples.pdf}
\includegraphics[width=8.3cm]{Mr19ABsamples.pdf}
\caption{
{\bf Left:} The $M_r<-19$ threshold sample projected correlation function with diagonal elements of 
covariance (points with errorbars). The grey lines are 50 randomly-selected HOD models that yield 
$\Delta \chi^2 <1$ compared to the best-fitting model. {\bf Right:} Same as the left panel but using a 
fit to a Decorated HOD model that contain parameters to describe the strength of assembly bias.
}
\label{fig:Mr19samples}
\end{center}
\end{figure*}
%---------------------------------------------------------------------------------------------------------------------------------

>>>>

correlated (anticorrelated) with halo concentration at fixed $\mvir.$ 
Thus the $A_{\rm cen,sat}$ parameters span the range $[-1, 1].$ 

@@

%----------------------------------------------------------------------------------------------------------------------------------
\begin{figure*}
\begin{center}
\includegraphics[width=8.3cm]{Mr19samples.pdf}
\includegraphics[width=8.3cm]{Mr19ABsamples.pdf}
\caption{
{\bf Left:} The $M_r<-19$ threshold sample projected correlation function with diagonal elements of 
covariance (points with errorbars). The grey lines are 50 randomly-selected HOD models that yield 
$\Delta \chi^2 < 5.89$ compared to the best-fitting model. For a Gaussian posterior distribution, 
$\Delta \chi^2 = 5.89$ would contain 68\% of the probability in the full five-dimensional parameter 
space. {\bf Right:} Same as the left panel but using a 
fit to a Decorated HOD model that contain parameters to describe the strength of assembly bias.
}
\label{fig:Mr19samples}
\end{center}
\end{figure*}
%---------------------------------------------------------------------------------------------------------------------------------
